mathml: Translate R expressions to MathML and LaTeX/MathJax

### 2022-12-13 Draft3.Rmd
latex/box

```{r add, echo=FALSE}
op <- list(left=quote(add_left(a + b)), right=quote(add_right(a + b)))
m <- lapply(op, FUN=mathjax, flags=list(cat=FALSE))

op <- as.character(op)

if(knitr::is_latex_output())
op <- sapply(op, FUN=knitr:::escape_latex)
if(knitr::is_html_output())

op <- sapply(op, FUN=knitr:::escape_html)
t <- cbind(Operator=op, Output=m)

>>>>

```{r add, echo=FALSE}
op <- list(left=quote(add_left(a + b)), right=quote(add_right(a + b)))
m <- lapply(op, FUN=mathout, flags=list(cat=FALSE))

op <- as.character(op)
if(knitr::is_latex_output())
  op <- sapply(op, FUN=knitr:::escape_latex)
if(knitr::is_html_output())
  op <- sapply(op, FUN=knitr:::escape_html)
t <- cbind(Operator=op, Output=m)
